Transforming Trash as an Artistic Act

### 2016-01-08 chapter2_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

%
%
\section{Throw away culture}

@@

\begin{singlespace}
\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips. \citep{strasser1999waste}
\end{quote}
\end{singlespace}

@@

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

@@

@@

% ARTWORK
% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
  \label{fig:RubySilvious_TeaBag}
\end{figure}

@@

% ARTWORK
% COFFEE CUP
% FROM http://www.gwynethleech.com/
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
  \caption{Installation view}
  \label{fig:GwynethLeech_Installation}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
  \caption{Painting in the public}
  \label{fig:GwynethLeech_Public}
\end{subfigure}
\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
\label{fig:GwynethLeech_CoffeeCups}
\end{figure}

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/SongDong_WasteNot.jpg}
  \caption{Song Dong, Waste Not, 1990}
  \label{fig:SongDong_WasteNot}
\end{figure}

@@

\begin{singlespace}
\begin{quote}
My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death. I recognised that in this era of transition, a person could live through several different lives in just one lifetime. In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
\end{quote}
\end{singlespace}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
  \caption{Tracey Emin, My Bed, 1998}
  \label{fig:TraceyEmin_MyBed}
\end{figure}

@@

\begin{singlespace}
\begin{quote}
In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects \citep[5]{hawkins2005ethics}.
\end{quote}
\end{singlespace}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
  \caption{Thompson’s Rubbish Theory}
  \label{fig:rubish_theory}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/Cesar_Zim.jpg}
  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
  \label{fig:Cesar_Zim}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
  \caption{Marcel Duchamp, Fountain, 1917}
  \label{fig:Duchamp_Fountaine}
\end{figure}

@@

>>>>

%
%
\section{Throw Away Culture}

@@

\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips. \citep{strasser1999waste}
\end{quote}

@@

% ARTWORK
% Portraits of Global Mass culture
%\begin{figure}[h!]
%\begin{subfigure}{.48\textwidth}
%  \centering
%  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
%  \caption{Original view}
%  \label{fig:ChrisJordan_Numbers_CloseView}
%\end{subfigure}
%\hfill
%\begin{subfigure}{.48\textwidth}
%  \centering
%  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
%  \caption{Close view}
%  \label{fig:ChrisJordan_Numbers_OriginalView}
%\end{subfigure}
%\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
%\label{fig:ChrisJordan_Numbers_CapsSeurat}
%\end{figure}

@@

% John Scanlan's book, On Garbage shows how western progress always has cleared away and discarded what went before; not only material waste but also knowledge. He believes that by examining our garbage we can gain useful insight into the condition of contemporary life.

@@

% ARTWORK
% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
%  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
%  \label{fig:RubySilvious_TeaBag}
%\end{figure}

@@

% ARTWORK
% COFFEE CUP
% FROM http://www.gwynethleech.com/
%\begin{figure}[h!]
%\begin{subfigure}{.48\textwidth}
%  \centering
%  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup5.jpg}
%  \caption{Installation view}
%  \label{fig:GwynethLeech_Installation}
%\end{subfigure}
%\hfill
%\begin{subfigure}{.48\textwidth}
%  \centering
%  \includegraphics[width=\linewidth]{graphics/Gwyneth-Leech-cup3.jpg}
%  \caption{Painting in the public}
%  \label{fig:GwynethLeech_Public}
%\end{subfigure}
%\caption{Gwyneth Leech, 365 A Year in Cups, 2013, Mixed media on upcycled paper coffee cups, Dimensions variable}
%\label{fig:GwynethLeech_CoffeeCups}
%\end{figure}

@@

% the installation consists of the complete contents of her home, amassed over fifty years during which the Chinese concept of wu jin qi yong, or "waste not," was a prerequisite for survival. The assembled materials, ranging from pots and basins to blankets, oil flasks, and legless dolls, form a miniature cityscape that viewers can navigate around and through.

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=8cm]{graphics/SongDong_WasteNot.jpg}
%  \caption{Song Dong, Waste Not, 1990}
%  \label{fig:SongDong_WasteNot}
%\end{figure}

@@

\begin{quote}
My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death. I recognised that in this era of transition, a person could live through several different lives in just one lifetime. In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
\end{quote}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/tracey-emin-my-bed.jpg}
%  \caption{Tracey Emin, My Bed, 1998}
%  \label{fig:TraceyEmin_MyBed}
%\end{figure}

@@

\begin{quote}
In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects \citep[5]{hawkins2005ethics}.
\end{quote}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=4cm]{graphics/rubbish_theory.jpg}
%  \caption{Thompson’s Rubbish Theory}
%  \label{fig:rubish_theory}
%\end{figure}

@@

% Bu iş dolaşımdaki olan bir şeyi alıp, onu çöpleştiriyor. Ama bunu yapması ile birlikte yapıldığı bağlam, hikayesi, çevresindeki insanlar, sanatçı hepsi birlikte onu müzede sergilenen, açık arttırmaya çıkar hale getiriyor.

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=10cm]{graphics/Cesar_Zim.jpg}
%  \caption{César, Compression Zim, 1960-1961, 157 x 82 x 64 cm}
%  \label{fig:Cesar_Zim}
%\end{figure}

@@

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/Duchamp_Fountaine.jpg}
%  \caption{Marcel Duchamp, Fountain, 1917, Porcelain urinal}
%  \label{fig:Duchamp_Fountaine}
%\end{figure}

### 2016-01-08 chapter3_reduced.tex
fixing errors
Former-commit-id: cb1fa634f5502bfce534528cc9f2324c88009894
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/picasso_chair.png}
  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
  \label{fig:Picasso_Chair}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
  \label{fig:Duchamp_BicycleWheel}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/amelie_01.jpg}
  \caption{Still image from Amélie}
  \label{fig:Amelie}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
  \caption{Dick Jewell, Found Photos, 1978}
  \label{fig:DickJewell_FoundPhotos}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
  \caption{Filomena Cruz, Road Kill, 2014, Photography}
  \label{fig:FilomenaCruz_RoadKill_ReVista}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:landfill_harmonic-sax}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:landfill_harmonic-violin}
    \end{subfigure}
    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
  \label{fig:Alsbrooks}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
  \caption{Michael Landy, Art Bin, 2014}
  \label{fig:MichaelLandy_ArtBin}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
  \caption{Michael Landy, Break Down, 2001}
  \label{fig:MichaelLandy_BreakDown}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/AgnesVarda_Potatoes.jpg}
  \caption{Still image from The Gleaners and I}
  \label{fig:AgnesVarda_Potatoes}
\end{figure}

>>>>

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/picasso_chair.png}
%  \caption{Pablo Picasso, Still Life with Chair Caning, 1912, oil on oil-cloth over canvas edged with rope, 29 x 37 cm (Musée Picasso)}
%  \label{fig:Picasso_Chair}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/duchamp-bicycle-wheel-1913.jpg}
%  \caption{Marcel Duchamp, Bicycle Wheel, 1913 (authorised reproduction 1951, original lost)}
  %\label{fig:Duchamp_BicycleWheel}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/amelie_01.jpg}
%  \caption{Still image from Amélie}
%  \label{fig:Amelie}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/DickJewell_FoundPhotos.jpg}
%  \caption{Dick Jewell, Found Photos, 1978}
%  \label{fig:DickJewell_FoundPhotos}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/TimGaudreau_SelfPotraitRevealedByTrash.jpg}
%  \caption{Tim Gaudreau, Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006}
%  \label{fig:TimGaudreau_SelfPotraitRevealedByTrash}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
%  \caption{Filomena Cruz, Road Kill, 2014, Photography}
%  \label{fig:FilomenaCruz_RoadKill_ReVista}
%\end{figure}

@@

% TODO resim yanlış
%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=10cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
%  \caption{Vic Muniz, Ironing Woman (Isis), 2008, mixed media, }
%  \label{fig:VicMuniz_PicturesOfGarbage}
%\end{figure}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
%        \caption{Sax}
%        \label{fig:landfill_harmonic-sax}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
%        \caption{Violin}
%        \label{fig:landfill_harmonic-violin}
%    \end{subfigure}
%    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=8cm]{graphics/Alsbrooks.jpg}
%  \caption{Kim Alsbrooks, Gen. Jefferson Davis, 2015, oil on aluminum can}
%  \label{fig:Alsbrooks}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=8cm]{graphics/MichaelLandy_ArtBin.jpg}
%  \caption{Michael Landy, Art Bin, 2014}
%  \label{fig:MichaelLandy_ArtBin}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=7cm]{graphics/MichaelLandy_BreakDown.jpg}
%  \caption{Michael Landy, Break Down, 2001}
%  \label{fig:MichaelLandy_BreakDown}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{graphics/AgnesVarda_Potatoes.jpg}
%  \caption{Still image from The Gleaners and I}
%  \label{fig:AgnesVarda_Potatoes}
%\end{figure}

### 2016-01-08 chapter4_reduced.tex
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

\begin{figure}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
    \end{subfigure}
    \caption{Examples of early works}
    \label{fig:EarlyWorks}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
  \caption{Recycling notice on the package}
  \label{fig:NoteOnPackage}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
  \caption{The banner carried by new grads, 2011}
  \label{fig:Banner_1}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
    \end{subfigure}
    \caption{Experiments with collected papers}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
        %\caption{}
        \label{fig:exhibition1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
        %\caption{}
        \label{fig:exhibition2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
        %\caption{}
        \label{fig:exhibition3}
    \end{subfigure}
    \caption{Installation experiments with models}
    \label{fig:exhibition}
\end{figure}

@@

\begin{figure}[!tbp]
  \centering
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
    \caption{Library}
    \label{fig:BilkentLibrary}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
    \caption{Computer Laboratory}
    \label{fig:BilkentLaboratory}
  \end{minipage}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
    \end{subfigure}
    \caption{Sample placement at Torun}
    \label{fig:ExperimentWithPaper}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
  \caption{Sample of QR code and notebook serial}
  \label{fig:Banner_1}
\end{figure}

>>>>

%\begin{figure}
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
%    \end{subfigure}
%    \caption{Examples of early works}
%    \label{fig:EarlyWorks}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
%  \caption{Recycling notice on the package}
%  \label{fig:NoteOnPackage}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
%  \caption{The banner carried by new grads, 2011}
%  \label{fig:Banner_1}
%\end{figure}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
%    \end{subfigure}
%    \caption{Experiments with collected papers}
%    \label{fig:ExperimentWithPaper}
%\end{figure}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
        %\caption{}
%        \label{fig:exhibition1}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.31\textwidth}
 %       \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
        %\caption{}
  %      \label{fig:exhibition2}
   % \end{subfigure}
    %\hfill
    %\begin{subfigure}[b]{0.31\textwidth}
     %   \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
        %\caption{}
      %  \label{fig:exhibition3}
    %\end{subfigure}
    %\caption{Installation experiments with models}
    %\label{fig:exhibition}
%\end{figure}

@@

%\begin{figure}[!tbp]
%  \centering
%  \begin{minipage}[b]{0.48\textwidth}
%    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
%    \caption{Library}
%    \label{fig:BilkentLibrary}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[b]{0.48\textwidth}
%    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
%    \caption{Computer Laboratory}
%    \label{fig:BilkentLaboratory}
%  \end{minipage}
%\end{figure}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
%    \end{subfigure}
%    \caption{Sample placement at Torun}
%    \label{fig:ExperimentWithPaper}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
%  \caption{Sample of QR code and notebook serial}
%  \label{fig:Banner_1}
%\end{figure}
